---
title: "Week 3 Assignment"
author: "Nguyen"
date: '2022-03-02'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Instructions

Create a web page presentation using R Markdown that features a plot created with Plotly. 

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a plot created with Plotly. 

We would love to see you show off your creativity! 

### Review criteria

The rubric contains the following two questions:

1. Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?

2. Is the web page a presentation and does it feature an interactive plot that appears to have been created with Plotly?

## My Leaflet map
### Some universities in Hanoi
#### Created on 02 March 2022

```{r, echo=FALSE}
library(plotly)

data <- read.csv("https://raw.githubusercontent.com/plotly/datasets/master/school_earnings.csv")

fig <- plot_ly(data, x = ~Men, y = ~Women, text = ~School, type = 'scatter', mode = 'markers',
        marker = list(size = ~Gap, opacity = 0.5, color = "green"))
fig <- fig %>% layout(title = 'Gender Gap in Earnings per University in the US in 2022 (unit: $US000s/year)',
         xaxis = list(showgrid = FALSE, title = "Men's salary"),
         yaxis = list(showgrid = FALSE, title = "Women's salary"))
fig
```

